The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-06 writing/draft3/draft8.tex
more literature and writing

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature. Only some of them were found significant predictors of maize yield. These include: Total seasonal precipitation and 
\subsection{Statistical approach}

@@

\color{blue}
\begin{itemize}
\item Add a description of residual and other diagnostic tests (AIC, VIF, autocorrelation)
\item Describe the procedure that I have applied to find the preferred combination of fixed effects and random effects
\item Describe the procedure that I have applied to find the preferred way of modelling the  correlation structure in errors (ARMA errors)
\end{itemize}
\color{black}

@@

\item If we get the yield data for the period from $2015$ onwards: Out of sample predictions and comparison with the real data
\end{itemize}

>>>>

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature including indicators of floods. Only some of them were found significant in our models. The significant measures include: Total seasonal precipitation and its squared values, average seasonal temperature, coefficient of variation of seasonal precipitation, standard deviation of average seasonal temperature \footnote{In case of temperature, we used standard deviation rather than coefficient of variation because temperature is measured on an interval scale and the coefficient of variation does not have any meaning for this type of data. },  maximum length of dry spell in number of days and the number of dry spell lasting for four days or more (a dry day is defined as day with precipitation less than $1$mm). We did not include squared values of the average seasonal temperature as it was not significant.
\subsection{Statistical approach}

@@

\color{blue}
\begin{itemize}
\item Add a description of residual and other diagnostic tests (AIC, autocorrelation)
\item Describe the procedure that I have applied to find the preferred combination of fixed effects and random effects
\item Describe the procedure that I have applied to find the preferred way of modelling the  correlation structure in errors (ARMA errors)
\end{itemize}
\color{black}

@@

\item show VIF
\item If we get the yield data for the period from $2015$ onwards: Out of sample predictions and comparison with the real data
\end{itemize}
